---
title: "multiOutliers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{multiOutliers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qacOutliers)
```

## kNN

information on the kNN method

## LoF

information on the LoF method

## Mahalanobis 

information on the mahalanobis method 

## iForest 

iForest stands for isolation forest. First, it randomly selects a variable, then randomly selects a value of that variable. This will work for both quantitaive and categorical; if the variable is quantitative, it will randomly pick a number in the range of the variable, and if the variable is categorical it will randomly pick a level. Then it will split the data using the value randomly selected eariler. 

The iForest method repeats the above steps until all points are separatly in their own node. Then, for each data point, it counts how many splits were needed to isolate it. 

Because the selection of variables and values is random, this process will return different results each time. Therefore, isolation trees are repeated many times and the results are averaged over all trials. More isolated points will have lower average path lengths. They are more isolated from the rest of the data's distribution, therefore they are called outliers. 


